---
title: "CSC 8631 Report"
author: "Harvey"
date: "24/11/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir= normalizePath('..'))
```

```{r ProjectTemplate, include=FALSE}
library(ProjectTemplate)
load.project()
```

## Aim and Objective

The aim of this analysis is to explore and see if there is any correlation between the time spent watching the course videos and the scores the student receives, collectively as a group, over the section. 

In addition to this, we will look to find the students that are having the hardest time with the multiple choice questions and look to provide extra support/help and to intervene at the earliest stage possible by reviewing the number of times the student has gotten the incorrect score as part of the question response.



<!-- ## Including Plots -->

<!-- You can also embed plots, for example: -->

<!-- ```{r pressure, echo=FALSE} -->
<!-- plot(pressure) -->
<!-- ``` -->

<!-- Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot. -->
